Whole-field total density measurements by Digital Image Correlation \thanks{Grants or other notes about the article that should go on the front page should be placed here. }

### 2020-02-21 Article/experimentsInFluids.tex
Compensation

\section{Digital Image Correlation}
\label{sec:DIC}
Digital Image Correlation (DIC) is a technique \cite{sutton2009image} to obtain deformation maps from images. We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations. To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines}. To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD \cite{sutton2009image}. We solve this nonlinear least-squares problem  by (1) providing an initial guess and (2) solving an iterative scheme. As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy. After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses. As iterative scheme we use the LM algorithm.

\begin{table}[htbp]
\caption{Digital Image Correlation parameters.}
\label{tab:esterrmagn}
\centering
\begin{tabular}{ll}
Noise & \\
Subset Size & \\
Grid Size 	& 5 \\
Measurements Points & \\
Total Number of Images & \\
Number of Averaged Images & \\
Displacements & \\
\qquad Spatial Resolution & x pixels, x mm \\
\qquad Resolution & 0.0105 pixels (x mm) \\
Index of Refraction & \\
\qquad Smoothing Method & \\
\qquad Resolution & x \\
\end{tabular}
\end{table}

@@

Since we are working with liquids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$ \cite{lorentz1916theory, tan2015dependence},
\begin{equation}
 	\frac{n^2-1}{n^2+2} \frac{1}{\rho} = \mbox{ constant}.
\end{equation}
We use our calibration measurement to determine the constant: $\rho=1$ for $n=1.333$.

@@

\begin{figure}[htbp]
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{Reference Image: Filled with air}\label{fig:air0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
	\subcaption{Calibration Image Image: Filled with water with known $n$}\label{fig:fresh0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:twolayer0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
	\subcaption{Index of Refraction $n$ for Calibration Image}\label{fig:ncalibration0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{$\Delta x$ from DIC}\label{fig:dx0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
		\subcaption{$\Delta y$ from DIC}\label{fig:dy0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:ndeformed0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
		\subcaption{Correlation Coefficient from DIC}\label{fig:C0side}
\end{subfigure} \\
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
		\subcaption{$n$ profiles for Calibration and Deformed Images}\label{fig:nprofiles0side}
\end{subfigure}
\caption{The procedure for obtaining the index of refraction field $n$. We obtain three images: one Reference Image (\ref{fig:air0side}) filled with air, one Calibration Image (\ref{fig:fresh0side}) filled with water without salts and one Deformed Image (\ref{fig:twolayer0side}) filled with water with an unknown $n$-field. Applying DIC between the Reference Image and the Correlation image, we find the displacements $D=(\Delta x, \Delta y)$. Using these displacements $D$ in (\ref{eq:calmin}), we obtain the parameters $\underline{\alpha}$. After calibration, the resulting $n$-field is uniform (\ref{fig:ncalibration0side}). Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).  Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}). Horizontally averaging the index of refraction fields $n$ yields the profiles in \ref{fig:nprofiles0side}.}
\label{fig:0side}
\end{figure}

@@

In the second application, Figure \ref{fig:0side}, we measured the background density of a continuously stratified fluid. We filled a tank through the double bucket method. After taking a Reference Image, a Calibration Image and a Deformed Image, we repositioned the camera for a Synthetic Schlieren measurement. After oscillating the tank, we measured the angles of the internal waves propagating in the fluid. Table \ref{tab:SSintwav} shows the forcing frequencies $\omega$ and angles $\beta$. Through
\begin{equation}
	N = \omega \cos \beta
\end{equation}
we determined the buoyancy frequency $N$. Through
\begin{equation}
	N^2 = - \frac{g}{\rho_0}\frac{d \rho_0}{d z}
\end{equation}
we determined the buoyancy frequency $N$, obtained from our new method.

\begin{figure}[htbp]
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:strat0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
		\subcaption{Correlation Coefficient from DIC}\label{fig:stratC0side}
\end{subfigure} \\
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{$\Delta x$ from DIC}\label{fig:stratdx0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{}
		\subcaption{$\Delta y$ from DIC}\label{fig:stratdy0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:stratndeformed0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{}
		\subcaption{Background Density $\rho_0$ for Deformed Image}\label{fig:stratrho0deformed0side}
\end{subfigure} 
\caption{Determining the background density for a continuously stratified fluid. After taking three images, with the Deformed Image \ref{fig:strat0side}, we obtain the displacements $\Delta x$ in Figure \ref{fig:stratdx0side} and $\Delta y$ in Figure \ref{fig:stratdy0side} from DIC. After calibration we obtain the index of refraction field $n$ in Figure \ref{fig:stratndeformed0side}. Using the Lorentz-Lorenz relation we obtain the density profile \ref{fig:stratrho0deformed0side} with buoyancy frequency $N$ of NUMBER. }
\label{figs:strat0side}
\end{figure}

@@

\section{Discussion}
\label{sec:dis}

>>>>

\section{Correction}
\label{sec:cor}
%\subsection{Permanent Compensation}
Region of Compensation: Sightly similar to \cite{tian2018accuracy} and \cite{pan2013high}

\section{Digital Image Correlation}
\label{sec:DIC}
Digital Image Correlation (DIC) is a technique \cite{sutton2009image} to obtain deformation maps from images. We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations. To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines}. To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD \cite{sutton2009image}. We solve this nonlinear least-squares problem  by (1) providing an initial guess and (2) solving an iterative scheme. As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy. After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{chen2009quality, pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses. As iterative scheme we use the LM algorithm.

\begin{table}[htbp]
\caption{Digital Image Correlation parameters corresponding to Figure \ref{fig:0side}.}
\label{tab:esterrmagn}
\centering
\begin{tabular}{ll}
Noise & \% \\
Subset Size & 41 pixels \\
Grid Size 	& 5 pixels \\
Measurement Points & $735 \times 415$ pixels \\
%Total Number of Images & \\
Number of Averaged Images & 240 \\
Displacements & \\
\qquad Spatial Resolution & x pixels, x mm \\
\qquad Resolution & 0.0105 pixels (x mm) \\
Index of Refraction & \\
\qquad Smoothing Method & \\
\qquad Resolution & x \\
\end{tabular}
\end{table}

@@

We use the experimental data from \cite{tan2015dependence} to relate the measured index of refraction to the density.

@@

\begin{figure}[htbp]
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{TL_air}
		\subcaption{Reference Image: Filled with air}\label{fig:air0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{TL_fresh}
	\subcaption{Calibration Image: Filled with water with known $n$}\label{fig:fresh0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{TL_TL}
		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:twolayer0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{Calibrationnsurf}
	\subcaption{Index of Refraction $n$ for Calibration Image}\label{fig:ncalibration0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{TL_DX}
		\subcaption{$\Delta x$ from DIC}\label{fig:dx0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{TL_DY}
		\subcaption{$\Delta y$ from DIC}\label{fig:dy0side}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{TwoLayernSurf}
		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:ndeformed0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{TwoLayerHorizontalAveraged}
		\subcaption{$n$ profiles for Calibration and Deformed Images}\label{fig:nprofiles0side}
\end{subfigure}
\caption{The procedure for obtaining the index of refraction field $n$. We obtain three images: one Reference Image (\ref{fig:air0side}) filled with air, one Calibration Image (\ref{fig:fresh0side}) filled with water without salts and one Deformed Image (\ref{fig:twolayer0side}) filled with water with an unknown $n$-field. Applying DIC between the Reference Image and the Correlation image, we find the displacements $D=(\Delta x, \Delta y)$. Using these displacements $D$ in (\ref{eq:calmin}), we obtain the parameters $\underline{\alpha}$. After calibration, the resulting $n$-field is uniform (\ref{fig:ncalibration0side}). Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}).  Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}). Horizontally averaging the index of refraction field $n$ yields the profiles (\ref{fig:nprofiles0side}).}
\label{fig:0side}
\end{figure}

@@

In the second application, Figure \ref{fig:0side}, we measured the background density of a continuously stratified fluid. We filled a tank through the double bucket method. After taking a Reference Image, a Calibration Image and a Deformed Image, we repositioned the camera for a Synthetic Schlieren measurement. After oscillating the tank, we measured the angles of the internal waves propagating in the fluid. Table \ref{tab:SSintwav} shows the forcing frequencies $\omega$ and angles $\beta$. Through
\begin{equation}
	\omega = N \cos \beta
\end{equation}
we determined the buoyancy frequency $N$. Through
\begin{equation}
	N^2 = - \frac{g}{\rho^*}\frac{d \rho_0}{d z}
\end{equation}
we determined the buoyancy frequency $N$, obtained from our new method. From Figure \ref{fig:stratrho0deformed0side} we see that $d \rho_0 / d z =\SI{ - 0.2}{\gram\per\cubic\centi\metre\per\metre}$. Taking a mean reference density $\rho^*$ of $\SI{1}{\gram\per\cubic\centi\metre}$, we find a buoyancy frequency of $N = \SI{1.4}{\radian\per\second}$.

\begin{figure}[htbp]
\begin{subfigure}{.5\linewidth}
\centering \includegraphics[width = \textwidth]{TL_strat}
		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:strat0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{strat_DX}
		\subcaption{$\Delta x$ from DIC}\label{fig:stratdx0side}
\end{subfigure} \\
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{strat_DY}
		\subcaption{$\Delta y$ from DIC}\label{fig:stratdy0side}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{Strat_DensityProfile}
		\subcaption{Background Density $\rho_0$ for Deformed Image}\label{fig:stratrho0deformed0side}
\end{subfigure} 
\caption{Determining the background density for a continuously stratified fluid. After taking three images, with the Deformed Image \ref{fig:strat0side}, we obtain the displacements $\Delta x$ in Figure \ref{fig:stratdx0side} and $\Delta y$ in Figure \ref{fig:stratdy0side} from DIC. After calibration we obtain an index of refraction field $n$ and density field $\rho$. Horizontally averaging the density field we obtain the density profile \ref{fig:stratrho0deformed0side} with buoyancy frequency $N = \SI{1.4}{\radian\per\second}$.}
\label{figs:strat0side}
\end{figure}

@@

\clearpage
\section{Discussion}
\label{sec:dis}
